Viscous Transport in Eroding Porous Media

### 2019-09-19 docs/transport/erosion_transport.tex
worked on abstract and pore size sections

\documentclass[preprint, 10pt]{elsarticle}

@@

\begin{abstract} 
  An abstract
\end{abstract}

\begin{keyword}
  Keyword 1 \sep Keyword 2 \sep Keyword 3 
\end{keyword}

@@

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  We construct a Delaunay triangulation with the centers of the
eroding bodies corresponding to the vertices of the triangles.  Then, if
the side of a triangle connects two vertices, we call the bodies
neighbors.  Then, for each pair of neighbors, we measure the distance
between the bodies.  Once a Delaunay triangulation is formed, it is used
for all subsequent time steps until a body completely disappears.  At
this point, a new Delaunay triangulation is formed.  {\color{red}In
Figure~\ref{fig:Eroding100gap_mean_var}, we record the gap distances
between bodies neighbors and calculate the mean and variance with
respect to porosities.  For the mean of gap distances, it is linearly
increacing until $\phi = 85\%$ which means the eroding .  For the
variance of gap distances, it is almost a constant function until $\phi=
85\%$  }
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
the variance of gaps in (b) with respect to porosity $\phi$ of an
eroding geometry initialized with 100 bodies . 
Red stars are six selected porosities to have the details of  
the disturbutions of gaps and fitting curves of the disturbutions 
in Figure~\ref{fig:Eroding100gap_hist}.}
\end{figure}

Finally, we investigate the effects of erosion on pore sizes.  The
distribution of the pore sizes can be directly related to the
distribution of the velocity, and thus effects the
tortuosity~\cite{den-ica-hid2018} and anomalous
dispersion~\cite{dea-qua-bir-jua2018}. In addition, the pore sizes are
required in network models~\cite{bry-mel-cad1993, bry-kin-mel1993}.  As
described in Section~\ref{sec:throats}, we use a Delaunay triangulation
to define neighboring eroding bodies, and we compute the throat size by
finding the closest distance between all neighboring bodies.  Once all
throat sizes are computed, we analyze their distribution as a function
of the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
histograms of the pore throat sizes at six porosities of the erosion
process. These distributions have been modelled with Weibull
distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
distribution with the same first two moments as the data.  The
parameters that parameterize the distribution, $(k,\lambda)$, are
included in the caption of Figure~\ref{fig:Eroding100gap_hist}.  In
Figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
of the throat sizes as a function of the porosity.  At low porosities,
the mean grows roughly linearly and the variance is roughly constant
until about porosity $\phi = 0.85$.  At this point, both the mean and
variance of the gap sizes quickly grow.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var} The mean (a) and variance
(b) of the gap sizes of an eroding geometry.  The red stars correspond
to the six porosities in Figure~\ref{fig:Eroding100gap_hist}.}
\end{figure}

>>>>

\documentclass[preprint,10pt]{elsarticle}

@@

\begin{abstract} 
  We extend our previous work, [Journal of Computational Physics, {\bf
  375}:1--21, 2018], to simulate dense suspensions of fluid-mechanical
  erosion of two-dimensional erosion of porous media. By using a
  Barycentric quadrature rule, we resolve interactions
  between nearly touching bodies without requiring an unfeasible number
  of discretization points.  Since the Barycentric quadrature rule is
  computationally expensive, it is only used when necessary, and the
  spectrally accurate trapezoid rule is used otherwise. Our final fluid
  solver only requires $\mathcal{O}(N)$ iterations per time step. Next,
  we simulate and analyze transport through eroded porous geometries.
  Our results demonstrate the effects of erosion on tortuosity,
  dispersion, and pore size distributions.
\end{abstract}

\begin{keyword}
  Porous media \sep Stokes flow \sep Erosion \sep Quadrature \sep
  Transport \sep Tortuosity \sep Anomalous dispersion \sep Pore size
  distributions
\end{keyword}

@@

Finally, we investigate the effects of erosion on pore sizes.  The
distribution of the pore sizes can be directly related to the
distribution of the velocity, and thus effects the
tortuosity~\cite{den-ica-hid2018} and anomalous
dispersion~\cite{dea-qua-bir-jua2018}. In addition, the pore sizes are
required in network models~\cite{bry-mel-cad1993, bry-kin-mel1993}.  As
described in Section~\ref{sec:throats}, we use a Delaunay triangulation
to define neighboring eroding bodies, and we compute the pore size by
finding the closest distance between all neighboring bodies.  Once all
pore sizes are computed, we analyze their distribution as a function
of the porosity.  In Figure~\ref{fig:Eroding100gap_hist}, we plot
histograms of the pore pore sizes at six porosities of the erosion
process. These distributions have been modelled with Weibull
distributions~\cite{ioa-cha1993}, and we superimpose the Weibull
distribution with the same first two moments as the data.  The
parameters that parameterize the distribution, $(k,\lambda)$, are
included in the caption of Figure~\ref{fig:Eroding100gap_hist}.  In
Figure~\ref{fig:Eroding100gap_mean_var}, we plot the mean and variance
of the pore sizes as a function of the porosity.  Interestingly, for
porosities less than $\phi = 85\%$, the mean pore size grows linearly
and the variance remains nearly flat. Since a channelized geometry has
large variance, this indicates that channelization is less prevalent at
low porosities.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var} The effect of erosion on the
mean (a) and the variance (b) of the pore sizes. The geometry initially
contains 100 eroding bodies.  The distributions of the pore sizes in
Figure~\ref{fig:Eroding100gap_hist} are indicated by the red stars.}
\end{figure}
